Polymers for Near-field Electrospinning with Spatial Control

### 2019-08-22 NFES_Review/article.tex
article progress

\title{Review of Polymer Solutions for Near-Field Electrospinning with Spatial Control
}

@@

The main components of the electrospinning technique are the fluid control unit (e.g. syringe pump) and a voltage power supply. The process also requires a target electrode or combination of electrodes on which the fibers can be collected.  Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}. Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning \unskip~\cite{527120:12033655}. Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}.

@@

\section{Polymer Solution}
In electrospinning, it is generally agreed that with higher concentration, the diameter of the fibers increased due to greater viscosity which resist stretching. In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased\unskip~\cite{527120:11974306,527120:11974329}. However, in separate studies by Pan et al.\unskip~\cite{527120:11974317,527120:12321129} using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration. Pan et al.\unskip~\cite{527120:12321129} attributed this to a higher charge accumulation in higher concentration PVDF solution. However, more studies need to be carried out to verify this.
\begin{table*}[!htbp]
\caption{{Approximation process to estimate the critical polymer concentration. Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.} }
\label{tw-8687dd17082c}
\def\arraystretch{1}
\ignorespaces 
\centering 
\begin{tabulary}{\linewidth}{LL}
\tbltoprule Observation & Concentration Adjustement\\
\tblmidrule 
Dripping, no stream &
  Increase\\
Splitting small droplets &
  Increase slightly\\
Steady stream &
  No concentration adjustment\\
Splitting large globs &
  Decrease slightly\\
Nozzle clogging  &
  Decrease\\
\tblbottomrule 
\end{tabulary}\par 
\end{table*}

@@

Poly(ethylene oxide) (PEO; MW = 4,000,000) &

@@

Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV; MW = 380,000) with Poly(ethylene oxide) (PEO; MW = 300,000) &

@@

  \textbf{Solution Concentration:} \mbox{}\protect\newline 10$mg $ of MEH-PPV in 2$mL $ of toluene; 500$mL $ of MEH-PPV solution with 250$mg $ of PEO in 3.5$mL $ of acetonitrile; 500$mL $ of MEH-PPV solution with 250$mg $ of PEO in 3$mL $ of acetic acid / toluene (17 / 83). The resulting MEH-PPV/PEO concentration is 1:100 \mbox{}\protect\newline \textbf{Nozzle:} mm-diameter tip Tungsten spinneret in a 26 gauge needle \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} SiO2/Si (oxide thickness = 800 nm) \mbox{}\protect\newline \textbf{Applied voltage:} around 1.3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 100$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} around 100$\mu m $ &

@@

Poly(ethylene oxide) (PEO) &

@@

Poly(vinylidine fluorid) (PVDF) &

@@

  \textbf{Solution Concentration:} 1.8$g $ PVDF in 4.1$g $ of DMF and 4.1$g $ of acetone. The resulting concentration is 18\% PVDF. \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 510$\mu m $ and inner diameter of 260$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 400$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 10-50$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Poly(dimethylsiloxane) (PDMS) on Ecoflex \mbox{}\protect\newline \textbf{Applied voltage:} 1.5{\textendash}3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0-400$mm/min $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 1.5-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

@@

Polyhedral Oligomeric Silsesquioxane-Poly(Carbonate-Urea)Urethane (POSS-PCU) and Polyhedral Oligomeric Silsesquioxane Poly(Caprolactone-Poly(Carbonate-Urea)Urethane) (POSS-PCL-PCU) &

@@

Poly(ethylene oxide) (PEO) &

@@

Poly(Vinylidene Fluoride) (PVDF) &

@@

Poly(9-Vinyl Carbazole) (PVK) &

@@

Polystyrene (PS) &

@@

  \textbf{Solution Concentration:} 1 to 5$wt\% $ PS \mbox{}\protect\newline \textbf{Nozzle:} Glass nozzle inner diameter of 2$\mu m $ and outer diameter of 2.66$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} Si \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: 20, 30, 40$\mu m $} \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} 500 to 400$V $ in 25$V $ increments \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.01-10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 60-170$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

@@

Poly(ethylene oxide) (PEO) &

@@

Poly(ethylene oxide) (PEO) &

@@

Gelatin \mbox{}\protect\newline (porcine skin) &

@@

  \textbf{Solution Concentration:} PEO concentrations of 16\% adn 18\% \mbox{}\protect\newline \textbf{Nozzle:} 40$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.36$m/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.15$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

@@

Poly(co-Glycolic) acid (PLGA)  &

@@

Poly(ethylene oxide) (PEO) with Tetrabutylammonium tetrafluoroborate (TBF) and SU-8 2002 &

@@

Poly(ethylene oxide) (PEO) &

@@

Poly(ethylene oxide) (PEO) &

@@

  \textbf{Solution Concentration:} 10$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 32G metal needle \mbox{}\protect\newline \textbf{Solution deposition rate:} (Jet impact speed of 5$mm/s $ ) \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 0.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} p-type silicon wafer \mbox{}\protect\newline \textbf{Applied voltage:} 400$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 5$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 50$\mu m $ &

@@

\subsection{Low-Voltage NFES (LV NFES) \unskip~\protect\cite{527120:11973130}}Some differences have been discovered between LV-NFES and conventional NFES. Low voltage near field electrospinning produces thinner fibers with lower voltages. Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching. Bisht et al. (2011) reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.

@@

\section{Conclusion}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{section}{\numberline{}\refname}}{}{}

>>>>

\title{Polymers for Near-field Electrospinning with Spatial Control
}

@@

\subsection{Types of electrospinning }The main components of the electrospinning technique are the fluid control unit (e.g. syringe pump) and a voltage power supply. The process also requires a target electrode or combination of electrodes on which the fibers can be collected.  Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}. Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning \unskip~\cite{527120:12033655}. Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}.

\subsubsection{High voltage power supply}Direct Current \mbox{}\protect\newline Alternating Current

\subsubsection{Polymer reservoir}Polymer melt \mbox{}\protect\newline Polymer solution

\subsubsection{Stretching forces}Centrifugal force \mbox{}\protect\newline Blowing forces \mbox{}\protect\newline Electric force \mbox{}\protect\newline Microfluidic forces \mbox{}\protect\newline Mechanical force

\subsubsection{Polymer yielding}Atomization (particles) \mbox{}\protect\newline Spraying (droplets) \mbox{}\protect\newline Spinning (fibers)

\subsubsection{Dispensing nozzle}Coaxial / Monoaxial \mbox{}\protect\newline Multinozzle

\subsubsection{Nozzle-to-substrate distance}Far Field Spinning \mbox{}\protect\newline Near Field Spinning

\section{"Electro - DC - monoaxial - solution - NF - spinning"}

@@

\section{Polymer Solution}
In electrospinning, it is typically agreed that the diameter of the fibers increased with higher concentration due to greater viscosity which withstands stretching. In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased\unskip~\cite{527120:11974306,527120:11974329}. However, in separate studies by Pan et al.\unskip~\cite{527120:11974317,527120:12321129} using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration.
\begin{table*}[!htbp]
\caption{{Approximation process to estimate the critical polymer concentration. Several polymer concentrations are tried and the resulting jets are observed until a continuous stream is achieved.} }
\label{tw-8687dd17082c}
\def\arraystretch{1}
\ignorespaces 
\centering 
\begin{tabulary}{\linewidth}{LL}
\tbltoprule Observation & Concentration Adjustement\\
\tblmidrule 
Dripping, no stream &
  Increase\\
Splitting small droplets &
  Increase slightly\\
Steady stream &
  No concentration adjustment\\
Splitting large globs &
  Decrease slightly\\
Nozzle clogging  &
  Decrease\\
\tblbottomrule 
\end{tabulary}\par 
\end{table*}

@@

Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) &

@@

Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV; MW = 380,000 $g/mol $) with Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &

@@

  \textbf{Solution Concentration:} \mbox{}\protect\newline 10$mg $ of MEH-PPV in 2$mL $ of toluene; 500$\mu L $ of MEH-PPV solution with 250$mg $ of PEO in 3.5$mL $ of acetonitrile / toluene (65 / 35); 500$\mu L $ of MEH-PPV solution with 250$mg $ of PEO in 3$mL $ of acetic acid / toluene (17 / 83). The resulting MEH-PPV/PEO concentration is 0.08 $wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} mm-diameter tip Tungsten spinneret in a 26 gauge needle \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L / h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} SiO2/Si (oxide thickness = 800 nm) \mbox{}\protect\newline \textbf{Applied voltage:} around 1.3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 50$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 100$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} around 100$\mu m $ &

@@

Poly(ethylene oxide) (PEO; MV = 300,000 $g/mol $) &

@@

Poly(vinylidine fluorid) (PVDF; MW = 440,000 $g/mol $) &

@@

  \textbf{Solution Concentration:} 1.8$g $ PVDF in 4.1$g $ of DMF and 4.1$g $ of acetone. The resulting concentration is 18\% PVDF. \mbox{}\protect\newline \textbf{Nozzle:} Needle outer diameter of 510$\mu m $ and inner diameter of 260$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 400$nL/min $ \mbox{}\protect\newline \textbf{Nozazle-to-substrate distance:} 10-50$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }Poly(dimethylsiloxane) (PDMS) on Ecoflex \mbox{}\protect\newline \textbf{Applied voltage:} 1.5{\textendash}3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0-400$mm/min $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 1.5-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

@@

Polyhedral Oligomeric Silsesquioxane-Poly(Carbonate-Urea)Urethane (POSS-PCU) and Polyhedral Oligomeric Silsesquioxane Poly(Caprolactone-Poly(Carbonate-Urea)Urethane) (POSS-PCL-PCU) \mbox{}\protect\newline (Dry Polycarbonate MW = 2000 $g/mol $) &

@@

Poly(ethylene oxide) (PEO; MW = 300,000 $g/mol $) &

@@

Poly(Vinylidene Fluoride) (PVDF; MW = 534,000 $g/mol $) &

@@

Poly(9-Vinyl Carbazole) (PVK; MW = 1,100,000 $g/mol $) &

@@

Polystyrene (PS; MW \textit{Not determined}) &

@@

  \textbf{Solution Concentration:} 1 to 5$wt\% $ PS \mbox{}\protect\newline \textbf{Nozzle:} Glass nozzle inner diameter of 2$\mu m $ and outer diameter of 2.66$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance}: 20, 30, 40$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition: }Si \mbox{}\protect\newline \textbf{Applied voltage:} 500 to 400$V $ in 25$V $ increments \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.01-10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 60-170$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

@@

Poly(ethylene oxide) (PEO; MW = 2,000,000 $g/mol $) &

@@

Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) &

@@

Gelatin \mbox{}\protect\newline (porcine skin; MW \textit{Not determined}) &

@@

  \textbf{Solution Concentration:} PEO concentrations of 16\% and 18\% \mbox{}\protect\newline \textbf{Nozzle:} 40$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.36$m/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.15$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &

@@

Poly(co-Glycolic) acid (PLGA; MW \textit{Not determined})  &

@@

Poly(ethylene oxide) (PEO; MW = 4,000,000 $g/mol $) with Tetrabutylammonium tetrafluoroborate (TBF; MW \textit{Not determined}) and SU-8 2002 &

@@

Poly(ethylene oxide) (PEO; 200,000 $g/mol $) &

@@

Poly(ethylene oxide) (PEO; MW = 400,000 $g/mol $) &

@@

  \textbf{Solution Concentration:} 10$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} 32G metal needle \mbox{}\protect\newline \textbf{Solution deposition rate:} (Jet impact speed of 5$mm/s $ ) \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 0.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} p-type silicon wafer \mbox{}\protect\newline \textbf{Applied voltage:} 400$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 5$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 50$\mu m $ &

@@

Nanofibers are fibers with diameters in the nanometer range. The development of nanofibers has greatly enhanced the scope for meeting up the modern world challenges.

Currently there are two types of electrospinning systems available for producing nanofiber: needle based electrospinning and needleless electrospinning. This paper summarizes the basic mechanism of various types of needle based and needleless spinning systems described in various literatures by many researchers.

\bgroup
\fixFloatSize{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}{\includegraphics{images/69d16de4-c7d7-4000-b4c8-93a40c79692b-uelectrospinningvariants.jpg}}{}
\makeatother 
\caption{{}}
\label{f-f076e2b74317}
\end{figure*}
\egroup

\subsection{Low-Voltage NFES (LV NFES) \unskip~\protect\cite{527120:11973130}}Some differences have been discovered between LV-NFES and conventional NFES. Low voltage near field electrospinning produces thinner fibers with lower voltages. Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching. Bisht et al. \unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.

@@

\section{Conclusion}

\bgroup
\fixFloatSize{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}{\includegraphics{images/fbd73f28-2c70-4a0a-be0b-f58ca8eab694-uweightconcentrationplot.png}}{}
\makeatother 
\caption{{}}
\label{f-ab38f7e015f7}
\end{figure*}
\egroup
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{NFES Achievements \& Challenges}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{section}{\numberline{}\refname}}{}{}
